Old is Still Gold: A Comparison of Cyber and Regular Consumer Fraud in The United States

### 2017-01-18 paper/paper.tex
minor edits

While cybercrime is a relatively recent human invention, fraudulent activity has a much longer history. This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud. Both categories of frauds experience a decrease during the holiday season. We study Interestingly, individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while 82\% of the cyber victims use an online resource to  generate fraud complaints.

@@

\textbf{Age:} While the differences in cyber and regular complaints remain fairly consistent, from Figure \cite{demographics} (a) we observe that individuals greater that 50 years complain significantly more than other age groups. Our significant regression values also corroborate to this trend.

>>>>

While cybercrime is a relatively recent human invention, fraudulent activity has a much longer history. This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud. We study the difference in fraud trends across time, location, ethnic and socio-economic factors. 
Both categories of frauds experience an overall decrease during the holiday season. Individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while a majority of cyber victims submit fraud complaints online. By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their operational methodologies to execute scams on the Internet that were initially perpetrated through traditional means.

@@

\textbf{Age:} While the differences in cyber and regular complaints remain fairly consistent, from Figure \ref{demographics} (a) we observe that individuals greater that 50 years complain significantly more than other age groups. Our significant regression values also corroborate to this trend.
